Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2021-04-08 main.tex
:pencil: Update numerical proof

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
% \usepackage{caption}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[RPvoltages]{circuitikz}
\usepackage[T1]{fontenc}
\usepackage[caption=false,font=footnotesize]{subfig}
% \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
% \usepackage[cmintegrals]{newtxmath}
\usepackage[short]{optidef}

@@

			Note that problem~\eqref{op:irs} is not a Semidefinite Programming (SDP) such that relaxing the rank constraint \eqref{co:irs_rank} has no analytical performance guarantee. In Section~\ref{se:performance_evaluation}, we prove through numerical simulations that the solution $\boldsymbol{\Phi}^{\star}$ to \ref{ob:irs} -- \ref{co:irs_sd} is rank-\num{1} under different configurations for all tested channel realizations. It suggests that the rank constraint \eqref{co:irs_rank} can be dropped with negligible loss and $\bar{\boldsymbol{\phi}}^\star$ can be directly obtained through eigen decomposition. In case $\boldsymbol{\Phi}^{\star}$ is not rank-\num{1}, a suboptimal solution can be extracted via the Gaussian randomization method \cite{Luo2010}. Specifically, we decompose $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Lambda}\boldsymbol{U}^H$, generate CSCG random vector $q \in \{1, \dots, Q\}$ by $\boldsymbol{\xi}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, construct the candidate $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Lambda}^{1/2}\boldsymbol{\xi}_q\right)}$, and choose the $\bar{\boldsymbol{\phi}}^\star$ that maximizes \eqref{ob:irs} as the solution. Finally, the phase shift of element $l$ is retrieved by $\theta_l^{\star}=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$. Problem~\eqref{op:irs} after rank relaxation can be solved by existing optimization tools such as CVX \cite{Grant2013}. The SCA algorithm of passive beamforming is summarized in Algorithm~\ref{al:sca}.
			\begin{algorithm}[!t]
				\caption{SCA: IRS Phase Shift.}
				\label{al:sca}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},\boldsymbol{w}_{\mathrm{I/P},n},\rho,\sigma_n,\bar{R},Q,\epsilon$, $\forall n$
					\State Construct $\boldsymbol{V},\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
					\State Get $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \ref{ob:irs} -- \ref{co:irs_sd}
						\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
					\If{$\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$}
						\State Get $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
					\Else
						\State Get $\boldsymbol{U},\boldsymbol{\Lambda}$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Lambda}\boldsymbol{U}^H$
						\State Generate $\boldsymbol{\xi}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $\forall q$
						\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Lambda}^{1/2}\boldsymbol{\xi}_q\right)},\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$, $\forall q$
						\State Set $q^{\star}=\arg\max_q{z(\boldsymbol{\Phi}_q)},\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
					\EndIf
					\State Set $\theta_l^\star=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$, $\forall l$, $\boldsymbol{\phi}^{\star}=[e^{j\theta_1^\star},\dots,e^{j\theta_L^\star}]^H$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
				\end{algorithmic}
			\end{algorithm}

@@

			\begin{proposition}\label{pr:bcd}
				Suppose $\boldsymbol{\Phi}$ is rank-\num{1}, every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star})$ provided by the BCD algorithm is a local optimal point of the original problem~\eqref{op:original}.
			\end{proposition}

@@

			Besides, minor modification is required for passive beamforming to cooperate with the low-complexity waveform schemes. To achieve the WIT point ($\eta=\rho=0$), the achievable rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized. To achievable non-WIT points, the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is now characterized by varying $\eta$, $\delta$ and $\rho$. Algorithm~\ref{al:lc} summarizes the modified passive beamforming design under low-complexity PS setup.

@@

			Similar to Algorithm~\ref{al:bcd}, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:lc}, the active beamforming $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ by \eqref{eq:wf}, \eqref{eq:smf} for TS or \eqref{eq:s_i}, \eqref{eq:s_p} for PS, until convergence. Similar to Proposition \ref{pr:bcd}, strict convergence and local optimality of the low-complexity BCD algorithm are guaranteed if $\boldsymbol{\Phi}$ is rank-\num{1}.
		\end{subsection}
	\end{section}

	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{layout.pdf_tex}
			\caption{System layout in simulation.}
			\label{fi:layout}
		\end{figure}
		To evaluate the performance of the proposed IRS-aided SWIPT system, we suppose a layout as Fig.~\ref{fi:layout} where the IRS moves along a horizontal line parallel to the AP-UE path. Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflective links. Consider a large open space Wi-Fi-like environment at center frequency \SI{5.18}{\GHz}, where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the reference path loss is \SI{-35}{\dB} at \SI{1}{\meter}. All channels are assumed NLoS with taps modelled as i.i.d. CSCG random variables of unit average sum-power, corresponding to a normalized multipath response. Rectenna parameters are chosen as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=50\,\si{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$. The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=36\,\si{\dBm}$ and the receive antenna gain is set to \SI{2}{\dBi}. For the algorithms, the tolerance is $\epsilon=10^{-8}$, the number of candidates for Gaussian randomization is $Q=10^{3}$, the scaling ratio is $\alpha=2$, and we assume $\delta=\rho$ for simplicity. All R-E regions are averaged over \num{300} channel realizations, and the $x$-axis has been normalized to per-subband rate $R/N$.

		We first provide numerical proof on the strict convergence and local optimality of the proposed BCD algorithms. Too see this, we define the eigen ratio as $\nu=\max_l\lambda_l(\boldsymbol{\Phi})/\sum_l\lambda_l(\boldsymbol{\Phi})$ where $\lambda_l(\boldsymbol{\Phi})$ is the $l$-th eigenvalue of $\boldsymbol{\Phi}$. Table~ shows the minimum value of $\nu$ during both BCD algorithms for all tested channel realizations.

		evaluate the rank of IRS matrix $\boldsymbol{\Phi}^\star$ obtained by Algorithm~\ref{al:sca} and \ref{al:lc}.

		We first evaluate the performance of Algorithm~\ref{al:sca} under SDR. It is demonstrated that $\boldsymbol{\Phi}^{\star}$ is rank-\num{1} for all tested channel realizations with different $M$, $N$ and $L$, such that $\boldsymbol{\phi}^{\star}$ can be directly obtained through eigen decomposition and the Gaussian randomization step is not required. Therefore, we claim Algorithm~\ref{al:sca} converges to stationary points of problem~\eqref{op:irs} without performance loss.

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_subband}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_subband.tex}
				}
			}
			\subfloat[WPT waveform amplitude\label{fi:waveform_subband}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/waveform_subband.tex}
				}
			}
			\caption{Average R-E region and WPT waveform amplitude versus $N$ for $M=1$, $L=20$, $\sigma_n^2=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
		\end{figure}

		Fig.~\ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$. \textit{First}, it is observed that increasing $N$ reduces the average per-subband rate $R/N$ but boosts the harvested energy. The reason is that the power budget is divided into smaller portions for each subband, but the number of balanced DC terms $m_\mathrm{P}$ is increased to boost the output DC current, as suggested by the scaling laws in \cite{Clerckx2018b}. Sorted waveform amplitudes in Fig.~\ref{fi:waveform_subband} also confirmed that, from the perspective of WPT, a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$. As shown in \eqref{eq:y_I4} and \eqref{eq:y_P4}, the only difference between modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of \num{2} and $\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gains. Therefore, the superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4). \textit{Second}, the R-E region is convex for $N = 2, 4$ and concave-convex for $N = 8, 16$. This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$. When $N$ is in between, the optimal strategy is a combination of both, i.e. a time sharing between the WPT point and the saddle SWIPT point obtained by PS (as the red curve in Fig.~\ref{fi:re_subband}). Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and transceiving mode, both heavily depends on $N$.

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/re_noise.tex}
			\end{adjustbox}
			\caption{Average R-E region and splitting ratio versus $\sigma_n^2$ for $M=1$, $N=16$, $L=20$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_noise}
		\end{figure}

		The influence of the average noise power on the average R-E region is investigated in Fig.~\ref{fi:re_noise}. \textit{First}, we note that for a large number of subbands, the R-E region is approximately concave for a high noise level while approximately convex for a low noise level. Hence, it can be concluded that TS is preferred at low SNR while PS is preferred at high SNR. This is because in the former case, the capacity-achieving WF algorithm tends to allocate more power to few strongest subbands. As the rate constraint $\bar{R}$ decreases, more subbands are activated to further boost the harvested DC power thanks to the balancing effect among different frequencies, which origins from the harvester nonlinearity. \textit{Second}, there exists a turning point in the R-E region especially for a small noise ($\sigma_n^2 \le -40\,\si{\dBm}$). The reason is that when $\bar{R}$ departs slightly from the maximum achievable rate, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocating more power to the multisine waveform, as a small-amplitude multisine could be inefficient for energy maximization. On the other hand, as $\bar{R}$ further reduces, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$, due to the advantage of multisine for efficient power transfer. The result highlights the benefit of dedicated power waveform and the necessity of joint optimization of waveform and splitting ratio.

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_distance}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_distance.tex}
				}
			}
			\subfloat[Path loss\label{fi:path_loss}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/path_loss.tex}
				}
			}
			\caption{Average R-E region and path loss versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{V}}=2\,\si{\meter}$.}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_tx}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_tx.tex}
				}
			}
			\subfloat[WIT SNR and WPT DC current\label{fi:scaling_tx}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/scaling_tx.tex}
				}
			}
			\caption{Average R-E region, WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n^2=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_{\mathrm{H}}=d_{\mathrm{V}}=0.5\,\si{\meter}$.}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_reflector}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_reflector.tex}
				}
			}
			\subfloat[WIT SNR and WPT DC current\label{fi:scaling_reflector}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/scaling_reflector.tex}
				}
			}
			\caption{Average R-E region, WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n^2=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=0.5\,\si{\meter}$.}
		\end{figure}

>>>>

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
% \usepackage{caption}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[RPvoltages]{circuitikz}
\usepackage[T1]{fontenc}
\usepackage[caption=false,font=footnotesize]{subfig}
% \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
% \usepackage[cmintegrals]{newtxmath}
\usepackage[short]{optidef}

@@

			Note that problem~\eqref{op:irs} is not a Semidefinite Programming (SDP) such that relaxing the rank constraint \eqref{co:irs_rank} has no analytical performance guarantee. In Section~\ref{se:performance_evaluation}, we prove through numerical simulations that the solution $\boldsymbol{\Phi}^{\star}$ to \ref{ob:irs} -- \ref{co:irs_sd} is rank-\num{1} under different configurations for all tested channel realizations. It suggests that the rank constraint \eqref{co:irs_rank} can be dropped with negligible loss and $\bar{\boldsymbol{\phi}}^\star$ can be obtained by eigen decomposition. In case $\boldsymbol{\Phi}^{\star}$ is not rank-\num{1}, a suboptimal solution can be extracted via the Gaussian randomization method \cite{Luo2010}. Specifically, we decompose $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Lambda}\boldsymbol{U}^H$, generate CSCG random vector $q \in \{1, \dots, Q\}$ by $\boldsymbol{\xi}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, construct the candidate $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Lambda}^{1/2}\boldsymbol{\xi}_q\right)}$, and choose the $\bar{\boldsymbol{\phi}}^\star$ that maximizes \eqref{ob:irs} as the solution. Finally, the phase shift of element $l$ is retrieved by $\theta_l^{\star}=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$. Problem~\eqref{op:irs} after rank relaxation can be solved by existing optimization tools such as CVX \cite{Grant2013}. The SCA algorithm of passive beamforming is summarized in Algorithm~\ref{al:sca}.
			\begin{algorithm}[!t]
				\caption{SCA: IRS Phase Shift.}
				\label{al:sca}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},\boldsymbol{w}_{\mathrm{I/P},n},\rho,\sigma_n,\bar{R},Q,\epsilon$, $\forall n$
					\State Construct $\boldsymbol{V},\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
					\State Get $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \ref{ob:irs} -- \ref{co:irs_sd}
						\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
					\If{$\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$}
						\State Get $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
					\Else
						\State Get $\boldsymbol{U},\boldsymbol{\Lambda}$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Lambda}\boldsymbol{U}^H$
						\State Generate $\boldsymbol{\xi}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $\forall q$
						\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Lambda}^{1/2}\boldsymbol{\xi}_q\right)},\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$, $\forall q$
						\State Set $q^{\star}=\arg\max_q{z(\boldsymbol{\Phi}_q)},\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
					\EndIf
					\State Set $\theta_l^\star=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$, $\forall l$, $\boldsymbol{\phi}^{\star}=[e^{j\theta_1^\star},\dots,e^{j\theta_L^\star}]^H$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
				\end{algorithmic}
			\end{algorithm}

@@

			\begin{proposition}\label{pr:bcd}
				Suppose $\boldsymbol{\Phi}$ is rank-\num{1}, every limit point $(\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star})$ provided by the BCD Algorithm \ref{al:bcd} is a local optimal point of the original problem~\eqref{op:original}.
			\end{proposition}

@@

			Besides, minor modifications are required for passive beamforming to cooperate with the low-complexity waveform schemes. To achieve the WIT point ($\eta=\rho=0$), the achievable rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized. To achievable non-WIT points, the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is now characterized by varying $\eta$, $\delta$ and $\rho$. Algorithm~\ref{al:lc} summarizes the modified passive beamforming design under low-complexity PS setup.

@@

			Similar to Algorithm~\ref{al:bcd}, we propose a Low-Complexity-BCD (LC-BCD) algorithm that iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:lc}, the active beamforming $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ by \eqref{eq:wf}, \eqref{eq:smf} for TS or \eqref{eq:s_i}, \eqref{eq:s_p} for PS, until convergence. Similar to Proposition~\ref{pr:bcd}, strict convergence and local optimality of the LC-BCD algorithm are guaranteed if $\boldsymbol{\Phi}$ is rank-\num{1}.
		\end{subsection}
	\end{section}

	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{layout.pdf_tex}
			\caption{System layout in simulation.}
			\label{fi:layout}
		\end{figure}
		To evaluate the performance of the proposed IRS-aided SWIPT system, we consider the layout in Fig.~\ref{fi:layout} where the IRS moves along a horizontal line parallel to the AP-UE path. Let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, and denote respectively $d_{\mathrm{D}}$, $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$ as the distance of direct, incident and reflective links. Consider a large open space Wi-Fi-like environment at center frequency \SI{5.18}{\GHz}, where the fading parameters follow IEEE TGn channel model D \cite{Erceg2004} and the reference path loss is \SI{-35}{\dB} at \SI{1}{\meter}. All channels are assumed NLoS with taps modelled as i.i.d. CSCG random variables of unit average sum-power, corresponding to a normalized multipath response. Rectenna parameters are chosen as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=\SI{50}{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$. The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=\SI{36}{\dBm}$ and the receive antenna gain is set to \SI{2}{\dBi}. For the algorithms, the number of candidates for Gaussian randomization is $Q=10^{3}$, the scaling ratio is $\alpha=2$, the tolerance is $\epsilon=10^{-8}$, and we assume $\delta=\rho$ for simplicity. All R-E regions are averaged over \num{300} channel realizations, and the $x$-axis is normalized to per-subband rate $R/N$.

		\begin{table*}[!t]
			\caption{The maximum value of $1-\nu$ over all R-E samples during BCD and LC-BCD algorithms for all tested channel realizations}
			\label{ta:eigen_ratio}
			\centering
			\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
			\hline
			\multicolumn{2}{|c|}{\multirow{2}{*}{}} & \multicolumn{3}{c|}{$M$} & \multicolumn{3}{c|}{$N$} & \multicolumn{3}{c|}{$L$} & \multicolumn{2}{c|}{$B$} \\ \cline{3-13}
			\multicolumn{2}{|c|}{} & \num{1} & \num{2} & \num{4} & \num{1} & \num{4} & \num{16} & \num{20} & \num{40} & \num{80} & \SI{1}{\MHz} & \SI{10}{\MHz} \\ \hline
			$\max(1 - \nu)$ & BCD & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{5.5511} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \cline{2-13}
			$[\times \num{e-16}]$ & LC & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{6.6613} & \num{8.8818} & \num{6.6613} & \num{6.6613} & \num{5.5511} \\ \hline
			\end{tabular}
		\end{table*}

		We first provide numerical proof on the strict convergence (thus local optimality) of both BCD algorithms. Too see this, we define the eigen ratio as $\nu=\max_l\lambda_l(\boldsymbol{\Phi})/\sum_l\lambda_l(\boldsymbol{\Phi})$ where $\lambda_l(\boldsymbol{\Phi})$ is the $l$-th eigenvalue of $\boldsymbol{\Phi}$. $\nu=1$ means $\boldsymbol{\Phi}$ is rank-\num{1}, and we claim $\boldsymbol{\Phi}$ is approximately rank-\num{1} when $1-\nu \approx 0$. Table~\ref{ta:eigen_ratio} shows the maximum value of $1-\nu$ over all R-E samples during both BCD algorithms. With reasonable precision, we conclude that $\boldsymbol{\Phi}$ is always rank-\num{1} under different configurations for all tested channel realizations. It suggests that the rank constraint \ref{co:irs_rank} can be dropped without performance loss, $\bar{\boldsymbol{\phi}}$ can be directly obtained through eigen decomposition, and the assumption of Proposition~\ref{pr:bcd} always hold such that both BCD algorithms converge to local optimal.

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_subband}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_subband.tex}
				}
			}
			\subfloat[WPT waveform amplitude\label{fi:waveform_subband}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/waveform_subband.tex}
				}
			}
			\caption{Average R-E region and WPT waveform amplitude versus $N$ for $M=1$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
		\end{figure}

		Fig.~\ref{fi:re_subband} illustrates the average R-E region versus the number of subband $N$. \textit{First}, it is observed that increasing $N$ reduces the per-subband rate $R/N$ but boosts the harvested energy. The reason is that the power budget is divided into smaller portions for each subband, but the number of balanced DC terms $m_\mathrm{P}$ is increased to boost the output DC current, confirming the scaling laws in \cite{Clerckx2018b}. Sorted waveform amplitudes in Fig.~\ref{fi:waveform_subband} also confirmed that, from the perspective of WPT, a dedicated multisine waveform is unnecessary for a small $N$ but is required for a large $N$. As shown in \eqref{eq:y_I4} and \eqref{eq:y_P4}, the only difference between modulated and unmodulated waveform on $z$ exists in the fourth-order terms, where $\mathbb{E}\left\{\mathbb{A}\left\{y_{\mathrm{I}}^4(t)\right\}\right\}$ has $N^2$ monomials with a modulation gain of \num{2} and $\mathbb{A}\left\{y_{\mathrm{P}}^4(t)\right\}$ has $(2N^3+N)/3$ monomials without modulation gains. Therefore, the superposed waveform enlarges the R-E region for a sufficiently large $N$ (typically no smaller than 4). \textit{Second}, the R-E region is convex for $N = 2, 4$ and concave-convex for $N = 8, 16$. This has the consequence that PS outperforms TS for a small $N$ and is outperformed for a large $N$. When $N$ is in between, the optimal strategy is a combination of both, i.e. a time sharing between the WPT point and the saddle SWIPT point obtained by PS (as the red curve in Fig.~\ref{fi:re_subband}). Compared with the linear harvester model that requires no dedicated power waveform and always prefer PS, the rectifier nonlinearity enlarges the R-E region by favoring a different waveform and transceiving mode, both heavily depends on $N$.

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_noise}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_noise.tex}
				}
			}
			\subfloat[Splitting ratio\label{fi:splitting_ratio_noise}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/splitting_ratio_noise.tex}
				}
			}
			\caption{Average R-E region and Splitting ratio versus $\sigma_n^2$ for $M=1$, $N=16$, $L=20$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{2}{\meter}$.}
		\end{figure}

		The influence of the average noise power on the R-E region is investigated in Fig.~\ref{fi:re_noise}. \textit{First}, we note that the R-E region is roughly concave/convex at low/high SNR such that TS/PS are preferred correspondingly. This is because the WF strategy tends to concentrate power on few strongest subbands at low SNR. As the rate constraint $\bar{R}$ decreases, more subbands are activated to further boost the harvested DC power thanks to the frequency compensation effect and harvester nonlinearity. \textit{Second}, there exists a turning point in the R-E region especially for a low noise level ($\sigma_n^2 \le \SI{-40}{\dBm}$). The reason is that when $\bar{R}$ departs slightly from the maximum value, the algorithm tends to adjust the splitting ratio $\rho$ rather than allocating more power to the multisine waveform, since a small-amplitude multisine could be inefficient for energy maximization. As $\bar{R}$ further decreases, a modulated waveform with a very large $\rho$ could be outperformed by a superposed waveform with a smaller $\rho$, owing to the high energy efficiency of multisine. The result highlights the benefit of superposed waveform and the necessity of joint waveform and splitting ratio optimization.

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_distance}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_distance.tex}
				}
			}
			\subfloat[Path loss\label{fi:path_loss}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/path_loss.tex}
				}
			}
			\caption{Average R-E region and path loss versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{V}}=\SI{2}{\meter}$.}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_tx}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_tx.tex}
				}
			}
			\subfloat[WIT SNR and WPT DC current\label{fi:scaling_tx}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/scaling_tx.tex}
				}
			}
			\caption{Average R-E region, WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$, $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{0.5}{\meter}$.}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_reflector}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_reflector.tex}
				}
			}
			\subfloat[WIT SNR and WPT DC current\label{fi:scaling_reflector}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/scaling_reflector.tex}
				}
			}
			\caption{Average R-E region, WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n^2=\SI{-40}{\dBm}$, $B=\SI{1}{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=\SI{0.5}{\meter}$.}
		\end{figure}
